---
title: "Presentation of application"
author: "Carine Alves"
date: "12/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This presentation contains documentation for the Diamond price prediction application. The application can be found [**here**] ( https://carinealves3112.shinyapps.io/CarineAlves/)

By building a linear regression model using `diamonds` data set, the price of a diamond is predicted depending of its properties.The application allows the user to select:

- Carat
- Cut
- Color
- Clarity

Builds a plot and gives predicted price of the diamond.

## Data used

The data used for this application is `diamonds` data set, which is part of `ggplot2` package.
This data set contains the information about 53940 diamonds with 10 variables:
```{r echo=FALSE}
library(ggplot2)
```

```{r echo=FALSE}
summary(diamonds)
```

## Shiny files

The application is build using Shiny package and the source code is in 2 files:

- `ui.R`
- `server.R`

The files can be found under the linkg: [GitHub repo](https://github.com/CarineLourencoAlves/Data-science-specialization_John-Hopckins-Developing-Data-products--Shiny-application)

## Application functionality
The application is drawing plot of diamonds in the `diamonds` data set distributed by their size (carat) and price ($). The regression line is shown on the plot as well. 

By selecting specific features of the diamond (carat, cut, clarity, color) the user is able to sub select the data set and the regression is recalculated based only on the diamonds in the data set that share the same features. If no features are selected the regression model is using all diamonds in the data set.

Below the graph the predicted price is shown.
